---
title: "Week 6 Sentiment_Analysis"
author: "Rob Wells"
date: "2025-03-05"
output: html_document
---

# Jour689 Spring 2025

For this exercise, you will use your project file dataframe to conduct a basic sentiment analysis of your articles


Step #1: load the following libraries: tidyverse, textdata, tidytext, quanteda, rio

```{r}



```


#import your "articles_df.csv" that contains the text of all of your articles in one dataframe. This is the spreadsheet we created last week in the "Text Compiler-Bigrams" exercise. 
```{r}
#import df 

```

#Tokenize sentence into a df, remove stopwords


```{r}
```


# Count the words in descending order
```{r}
# Word Count


```

# NRC Sentiment

NRC Lexicon on Whole Corpus
"The nrc lexicon categorizes words in a binary fashion (“yes”/“no”) into categories of positive, negative, anger, anticipation, disgust, fear, joy, sadness, surprise, and trust."
```{r}
# cite this lexicon
#install.packages("textdata")
nrc_sentiments <- get_sentiments("nrc")
afinn_sentiments <- get_sentiments("afinn")
```

#Count the NRC sentiments
```{r}

```

### Join the NRC Sentiments with the tokenized data


```{r}

sentiments_all <- text_tokenized %>%
  inner_join(nrc_sentiments) 

```

### Count Overall Sentiment with NRC

```{r}

```

## Use ggplot to chart Sentiments with the tokenized data

```{r}

```



# Create a new dataframe just with the NRC "anger" sentiment
```{r}


```

