---
title: "Key for R Proficiency"
author: "Rob Wells"
date: "2025-02-19"
output: html_document
---

#1: --Load relevant software libraries
```{r}
library(tidyverse)
library(rio)
library(janitor)
```

#2: Load the data: https://github.com/wellsdata/CompText_Jour/raw/main/data/blackindex_master.csv
```{r}

test <- rio::import("https://github.com/wellsdata/CompText_Jour/raw/main/data/blackindex_master.csv") |> 
  clean_names() |> 
    subset(select = -c(year)) #deleting year for the exercise below

```

#3: Using code, describe the number of rows and columns in the dataset

```{r}
dim(test)


# in this data set there are 1803 rows and 30 columns.. 


print(paste0("This dataset has ", nrow(test), " rows and ", ncol(test), " columns. Each row in this dataset appears to describe a single article that appeared in a Black newspaper between ", min(test$year), " and ", max(test$year), ". The articles appear to have been sourced from several historical newspaper databases and archives. Many of the article headlines reference racial terror lynching."))

```

#4: Create a table that displays a count of the top 20 newspaper_city entries. Filter out the NA values
```{r}
test %>% 
  filter(!is.na(newspaper_city)) |>
  count(newspaper_city) %>% 
 slice_max(order_by = n, n = 20)

```

#5: Create a table that counts all entries by year. Filter out the NA values
```{r}
library(lubridate)
test <- test |> 
  #mutate(date = as.Date(strptime(published_date, format = "%B %d, %Y %A"))) #some dates needed different processing
  mutate(date = as.Date(date, format = "%Y %m %d")) |> 
  mutate(year = year(date))


year_test <- test %>%
  group_by(year) %>%
  count()




test %>% 
  filter(!is.na(newspaper_city)) %>% 
  count(newspaper_city, year) %>% 
  arrange(desc(n)) 
  


```


#6: --Create a simple column ggplot chart that shows the total entries by year
```{r}
test %>%
  count(year) %>% 
  ggplot(aes(x = year, y = n, fill = n)) +
  geom_col() +
  scale_fill_gradient(low = "lightblue", high = "darkred") +
  theme(legend.position = "none") +
  labs(title = "Total articles by year in Black newspapers",
       subtitle = "There are more articles from 1920 in this dataset than any other year",
       x = "Year",
       y = "Total Articles",
       caption = "Source: Black Index Master Dataset, Chart by Rob Wells") +
  scale_x_continuous(breaks = seq(1850, 2020, 10)) +
  #rotate x axis labels 45 degrees
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```


# Extra items for discussion in class

## Checkinmg duplication in data
```{r}



trump_dei_news <- rio::import("https://github.com/wellsdata/CompText_Jour/raw/refs/heads/main/exercises/assets/data/trump_dei_news.XLSX") |> 
  clean_names()

#One way to check the duplication
trump_dei_news |>
  filter(!is.na(publication_4)) |> 
    filter(!is.na(publication_16)) |> 
  count(publication_4, publication_16)|> 
  top_n(20, n) |>
  arrange(desc( n))
```
#Cut columns
```{r}

#Ways to cut columns: 1) select just the columns you want: 

trim_trump <- trump_dei_news |> 
select(title, published_date,publication_location, publication_4, section, word_count,countries,  byline,company)
```

#Delete specific columns:

```{r}

trim_trump <- trim_trump |> 
  subset(select = -c(countries))
```


# Selecting specific variables
```{r}

test %>% 
  filter(newspaper_city == c("Chicago", "Pittsburgh", "Atlanta")) %>% 
  count(newspaper_city, year) %>% 
  arrange(desc(n)) 

```
#Filter out a city
```{r}

test %>% 
  filter(newspaper_city != "Chicago") %>% 
  count(newspaper_city, year) %>% 
  arrange(desc(n)) 

```

#Create a table that counts all newspaper_city entries by year
```{r}

entries_year <- test %>% 
  filter(!is.na(newspaper_city)) %>% 
  select(year, newspaper_city) %>% 
  group_by(year, newspaper_city) %>% 
  count(year) 

```

